### 2015-02-09 Projects/DelCo_2012/Report/DelCo_2012.tex
DelCo 2012: Updated report.

@@

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Spray_Hall}
	\caption{Hallway Nozzle Location}
	\label{fig:Hallway_Nozzle_Location}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Spray_Room}
	\caption{Room Nozzle Location}
	\label{fig:Room_Nozzle_Location}
\end{figure}

@@

@@

>>>>

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/DelCoBurnBuildingSpray}
	\caption{Nozzle Location for Gas Cooling Tests}
	\label{fig:Nozzle_Location_Gas_Cooling_Tests}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Spray_Hall}
	\caption{Hallway Nozzle Location for Fire Suppression Tests}
	\label{fig:Hallway_Nozzle_Location_Fire_Suppression_Tests}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Spray_Room}
	\caption{Room Nozzle Location for Fire Suppression Tests}
	\label{fig:Room_Nozzle_Location_Fire_Suppression_Tests}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Pictures/Single_Story_Instrumentation}
	\caption{Photograph of the Instrumentation in the Fire Suppression Tests.}
	\label{fig:Fire_Suppression_Instrumentation}
\end{figure}

@@

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Bars/BB1}
	\caption{Burn Building Test 1}
	\label{fig:Burn_Building_Test_1}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Bars/BB2}
	\caption{Burn Building Test 2}
	\label{fig:Burn_Building_Test_2}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Bars/BB3}
	\caption{Burn Building Test 3}
	\label{fig:Burn_Building_Test_3}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Bars/BB4}
	\caption{Burn Building Test 4}
	\label{fig:Burn_Building_Test_4}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Bars/BB5}
	\caption{Burn Building Test 5}
	\label{fig:Burn_Building_Test_5}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Bars/BB6}
	\caption{Burn Building Test 6}
	\label{fig:Burn_Building_Test_6}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Bars/BB7}
	\caption{Burn Building Test 7}
	\label{fig:Burn_Building_Test_7}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Bars/BB8}
	\caption{Burn Building Test 8}
	\label{fig:Burn_Building_Test_8}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Bars/BB9}
	\caption{Burn Building Test 9}
	\label{fig:Burn_Building_Test_9}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Bars/BB10}
	\caption{Burn Building Test 10}
	\label{fig:Burn_Building_Test_10}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Bars/BB11}
	\caption{Burn Building Test 11}
	\label{fig:Burn_Building_Test_11}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Bars/BB12}
	\caption{Burn Building Test 12}
	\label{fig:Burn_Building_Test_12}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Bars/BB13}
	\caption{Burn Building Test 13}
	\label{fig:Burn_Building_Test_13}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Bars/BB14}
	\caption{Burn Building Test 14}
	\label{fig:Burn_Building_Test_14}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Bars/BB15}
	\caption{Burn Building Test 15}
	\label{fig:Burn_Building_Test_15}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Bars/BB16}
	\caption{Burn Building Test 16}
	\label{fig:Burn_Building_Test_16}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Bars/BB17}
	\caption{Burn Building Test 17}
	\label{fig:Burn_Building_Test_17}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Bars/BB18}
	\caption{Burn Building Test 18}
	\label{fig:Burn_Building_Test_18}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Bars/BB19}
	\caption{Burn Building Test 19}
	\label{fig:Burn_Building_Test_19}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Bars/BB20}
	\caption{Burn Building Test 20}
	\label{fig:Burn_Building_Test_20}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Bars/BB21}
	\caption{Burn Building Test 21}
	\label{fig:Burn_Building_Test_21}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Bars/ES1}
	\caption{Experimental Structures Test 1}
	\label{fig:Experimental_Structures_Test_1}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Bars/ES2}
	\caption{Experimental Structures Test 2}
	\label{fig:Experimental_Structures_Test_2}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Bars/ES3}
	\caption{Experimental Structures Test 3}
	\label{fig:Experimental_Structures_Test_3}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Bars/ES4}
	\caption{Experimental Structures Test 4}
	\label{fig:Experimental_Structures_Test_4}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Bars/ES5}
	\caption{Experimental Structures Test 5}
	\label{fig:Experimental_Structures_Test_5}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Bars/ES6}
	\caption{Experimental Structures Test 6}
	\label{fig:Experimental_Structures_Test_6}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Bars/ES7}
	\caption{Experimental Structures Test 7}
	\label{fig:Experimental_Structures_Test_7}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Bars/ES72}
	\caption{Experimental Structures Test 7.2}
	\label{fig:Experimental_Structures_Test_7.2}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Bars/ES8}
	\caption{Experimental Structures Test 8}
	\label{fig:Experimental_Structures_Test_8}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Bars/ES9}
	\caption{Experimental Structures Test 9}
	\label{fig:Experimental_Structures_Test_9}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Bars/ES10}
	\caption{Experimental Structures Test 10}
	\label{fig:Experimental_Structures_Test_10}
\end{figure}

\begin{figure}[!ht]
	\includegraphics[width=6in]{../Figures/Bars/ES11}
	\caption{Experimental Structures Test 11}
	\label{fig:Experimental_Structures_Test_11}
\end{figure}
